Evolutionary rescue and reintroduction of resistant frogs allows recovery in the presence of a lethal fungal disease

### 2023-12-11 doc/manuscript/translocation.qmd
Provide the meta-analytic view, and minor edits in methods section

The splined window analysis identified 33 outlier regions for $\pi_{diff}$ and 58 outlier regions for *F~ST~* (@fig-spline-manhattan A, B).
Of these, 9 regions were outliers for both metrics ("shared regions") and 2 of these shared regions also contained one or more of the outlier SNPs described above.
A total of 33 annotated genes were found in the 9 shared regions (Datasets S3, S4).
Given this large number of genes, here we focus on those with the strongest signal of selection and/or immune-related functions.
The largest $\pi_{diff}$, indicative of directional selection, occurred in a 163kb region on Contig19, 12.9Mb upstream of the RIN3 outlier SNP (@fig-spline-manhattan C).
This region contains approximately 500 SNPs and one annotated gene called "interferon-induced very large GTPase 1-like" (GVINP1).
Additionally, a shared outlier region on Contig1 contained two complement factor genes (C6 and C7).
Interestingly, this region had a large negative $\pi_{diff}$ value, consistent with balancing selection.
Finally, one shared outlier region on Contig8 contained one outlier SNP (TCF19) and was within 360kb of another outlier SNP (VARS) (@fig-spline-manhattan D, @fig-synteny-plot).
This region (854kb from the beginning of the outlier window to the VARS SNP) contained a total of 8 annotated genes.
In *Xenopus*, five of these genes occur in the extended major histocompatibility complex (MHC) Class I region (FLOT1, TUBB, MDC1, CCHCR1, TCF19) and three occur in the extended MHC Class III region (HSP70, LSM2, VARS) [@ohta2006].
Therefore, this region under selection is part of the extended MHC Class I and III complex and shows synteny with other amphibian genomes.

@@

To identify important predictors of frog survival following translocation, we developed linear and multilevel models in a Bayesian framework.
Included predictor variables described characteristics of frogs, sites, and translocations (predictor variables: Bd load, sex, frog size, site elevation, winter severity in the year of translocation, winter severity in the year following translocation, donor population, day of year on which a translocation was conducted, and translocation order).
We used 1-year survival as a single metric of survival that was available for all translocated populations regardless of how many years of post-translocation data were available (range = 3--16).
Survival was rounded to integer values to produce a binomial outcome, and all models used a bernoulli family.
Group-level effects included site_id, translocation_id, or translocation_id nested within site_id.
We performed all analyses with the rstanarm package [@rstanarm2022] and R Statistical Software [v4.4.4, @rsoftware2022].
For all models, we used default, weakly informative priors, four chains, and 5000 iterations each for warmup and post-warmup.
We checked convergence of the MCMC algorithm using trace plots and Rhat, and evaluated model fit using leave-one-out ("LOO") cross-validation [@gelman2013; @gabry2019; @vehtari2016], as implemented by the loo package [@vehtari2022].

@@

>>>>

The splined window analysis identified 33 outlier regions for $\pi_{diff}$ and 58 outlier regions for *F~ST~* (@fig-spline-manhattan A, B).
Of these, 9 regions were outliers for both metrics ("shared regions") and 2 of these shared regions also contained one or more of the outlier SNPs described above.
A total of 33 annotated genes were found in the 9 shared regions (Datasets S3, S4).
Given this large number of genes, here we focus on those with the strongest signal of selection and/or immune-related functions.
The largest $\pi_{diff}$, indicative of directional selection, occurred in a 163kb region on Contig19, 12.9Mb upstream of the RIN3 outlier SNP (@fig-spline-manhattan C).
This region contains approximately 500 SNPs and one annotated gene called "interferon-induced very large GTPase 1-like" (GVINP1).
Additionally, a shared outlier region on Contig1 contained two complement factor genes (C6 and C7).
Interestingly, this region had a large negative $\pi_{diff}$ value, consistent with balancing selection.
Finally, one shared outlier region on Contig8 contained one outlier SNP (TCF19) and was within 360kb of another outlier SNP (VARS) (@fig-spline-manhattan D, @fig-synteny-plot).
This region (854kb from the beginning of the outlier window to the VARS SNP) contained a total of 8 annotated genes.
In *Xenopus*, five of these genes occur in the extended major histocompatibility complex (MHC) Class I region (FLOT1, TUBB, MDC1, CCHCR1, TCF19) and three occur in the extended MHC Class III region (HSP70, LSM2, VARS) [@ohta2006].
Therefore, this region under selection is part of the extended MHC Class I and III complex and shows synteny with other amphibian genomes.
<!--# Need to describe and reference Figures 14 SI and 15 SI. -->

@@

To identify important predictors of frog survival following translocation, we used multilevel Bayesian models.
We included predictor variables to describe characteristics of frogs, sites, and translocations (predictor variables: Bd load, sex, frog size, site elevation, winter severity in the year of translocation, winter severity in the year following translocation, donor population, day of year on which a translocation was conducted, and translocation order).
We used 1-year post-translocation survival estimates from mark-recapture models as the response, which was available for all translocated populations regardless of how many years of post-translocation data were available (range = 3--16).
Survival was rounded to integer values to produce a binary outcome, and modeled with a Bernoulli distribution.
Group-level effects included site_id, translocation_id, or translocation_id nested within site_id.
We performed all analyses with the rstanarm package [@rstanarm2022] and R Statistical Software [v4.4.4, @rsoftware2022].
For all models, we used default, weakly informative priors, four chains, and 5000 iterations each for warmup and post-warmup.
We checked MCMC convergence using trace plots and Rhat, and evaluated model fit using leave-one-out ("LOO") cross-validation [@gelman2013; @gabry2019; @vehtari2016], as implemented by the loo package [@vehtari2022].

@@

Finally, while it would theoretically be possible to estimate survival covariate effects in a joint mark-recapture model that integrates capture histories across all sites, this was impractical due to computational requirements of the mark-recapture models (namely, run time and memory). 
In modeling survival estimates from site-specific mark-recapture analyses, we are in effect conducting an among-site meta-analysis to better understand how site, cohort, and individual level characteristics explain variation in survival after translocation.
